Size-differentiated Export \add{Flux} in Different Dynamical Regimes in the Ocean

### 2020-06-26 Submission_and_reviews/response_to_reviewers.tex

%_____________________________________________
\begin{document}

% Article title and author
\begin{center}
\large
\textbf{
Response to reviewers\\}
\end{center}
\small

%\section{Response to Editor's comments}

%Comments provided by both reviewers are constructive, relevant, and thus greatly appreciated. We are grateful to those two reviewers for providing helpful comments that improved the clarity of the study.\\
We thank the reviewers for their constructive comments, which we have used to improve the manuscript in several ways. Most notable changes include:
\begin{itemize}
    \item Figures 7 and 8 are revised
    \item We have clarified the scientific reasoning behind some of the choices we made (e.g., particle seeding depth)
    \item We clarify that the range of sinking speeds selected for the study are comparable to the vertical velocities of the flow. It is the relative speed (between particle sinking and advection) that is important, as opposed to the absolute value of the sinking speed. Particles that sink faster are less affected by the flow.
    \item We argue that the export horizon can introduce bias and subjectivity \citep{Palevsky_2018, buesseler2020metrics} and thus keep our results in terms of fluxes.
\end{itemize}

@@

%Their comments led to major changes in the manuscript, namely figure 7 and 8. It also led us to clarify some of the aspects of the manuscript, such as the scientific reasoning behind some of the choices made (e.g., particle seeding depth). Most of the concerns risen by the reviewer were, however, related to either the definition of an export horizon to quantify export, or the range of sinking speeds selected for the study. We argue below that (1) based on both our work and recent studies \citep{Palevsky_2018}, the definition of an export horizon is not adequate and introduces subjectivity and biases in the results, and (2) the relevant range of sinking rates is scaled to the dynamics of the region. The absolute values are not so much what is important, but rather the relative importance to vertical currents. In a more energetic region than the northeast Pacific, the range of particle sinking speeds would be wider and reach sinking rates of O(100 m/day), but would lead to similar results than the ones detailed in this study.\\

The last two points were clarified in several parts of the revised manuscript. In addition, we respond to each of the reviewers' points (in blue).

@@

Additionally, we deliberately did not rely on an ``export depth horizon" due to the fact that it is not consistently defined in the literature. Recent work questions the validity of selecting a depth horizon as an ``export depth", arguing for a dynamics-based definition \citep{Palevsky_2018, buesseler2020metrics}. This is one of the reasons why the conclusions focus on export fluxes, rather than export, as the latter would require defining a possibly controversial export horizon.\\

@@

Based on this comment, the text has been modified in Section 2.2.2 to better justify the choices outlined above.}

\subsection*{Major point \#2}
\textit{Second, it is unclear why 5m/day is selected for the largest particle class. Studies using Underwater Vision Profilers reveal that a large portion of the particle flux is contributed by large aggregates of 0.1-5mm, which can have sinking speeds above 100m/day (see Guidi et al. 2008, Kiko et al. 2017). Comparing the summer and winter simulations, it seems that small particles only dominate the export flux when vertical advective velocities exceed the large particle sinking velocity. This condition would not be met if an aggregate particle class with sinking velocity of 100m/day were included. I suggest the inclusion of an additional "large aggregate" size class with appropriate sinking speed.\\}

{\color{blue}Thank you for this comment. We have now clarified that we refer to particles as ``fast (or slow)'' sinking if their sinking speed is fast (or slow) compared to the vertical velocities in the flow.} \\

\textit{``it is unclear why 5m/day is selected for the largest particle class."\\}
{\color{blue}
	The choice of 5 m/day sinking rates as the ``fast-sinking"  class (lines 300-301 of the original manuscript) is based on the PDFs of the advective vertical velocity. In our case, 5 m/day is faster than 85-90\% of the vertical velocity modeled in our domain at any given time. We have added text in Section 2.2.2 to make this clearer to the reader. It is worth noting that the region we model here has low eddy kinetic energy and weaker vertical velocities compared to frontal regions, or regions with deep mixed layers, such as the North Atlantic subpolar gyre.\\}

@@

\begin{equation}
	\frac{B_2w_2}{B_1w_1} >1 \quad \text{with} \quad w_2 > w_1
\end{equation}

Using Equation 8 in the main text, we obtain:
\begin{align}
	\frac{B_0\left(\frac{w_1}{w_0}\right)^{\frac{3-\xi}{2}}w_1}{B_0\left(\frac{w_2}{w_0}\right)^{\frac{3-\xi}{2}}w_2} &> 1\\[.2cm]
	\left(\frac{w_2}{w_1}\right)^{\frac{5-\xi}{2}} &>1
\end{align}
which is only true for $w_2 > w_1$ if $\xi<$5. In other words, if the Junge slope is larger than 5, the slopes of the particle size, biomass, AND biomass flux spectra are negative. While large, a value of $\xi>5$ is not unrealistic, as it falls within the range of $\xi$ obtained from satellite-based estimates \citep{Kostadinov_2009}.

It is generally true that for very large aggregates with sinking rates far exceeding the vertical velocities in the flow, the contribution of slower sinking particles is not dominant. Our study demonstrates the limitations of this paradigm as one considers slower-sinking particles classes. Furthermore, for the largest aggregate to constantly be driving the biomass flux, it would require a sustained production of those large particles. The biomass flux due to the aggregates would be larger, but the production of large aggregate particles is less sustained than small particles.   In fact, export from very fast sinking particles (e.g., 100 m /day) tends to occur as events and  not sustained in time \citep{Kiko_2017}.
Additionally, this paradigm is only true if the slope of the particle-size spectrum is smaller than 5 (based on our scaling).

Furthermore, the contribution of a fast-sinking (e.g. 100 m/day) class of particles to export fluxes can be computed theoretically (using $w \approx w_s$) and does not require any model simulations. We agree that this is important to consider and it is now discussed in the manuscript. We have added a paragraph in section 4.2 to address the contribution of aggregates sinking much faster than 5 m/day.}

@@

\subsection*{Major point \#3}
 \textit{Finally, the analysis demonstrated in Figures 7 and 8 does not seem appropriate for gauging the contribution of small and large particles to export, and the role of remineralization. As far as I understand, the insets in these figures show the flux associated with each particle class at 25 days after the particle release, computed based on their abundance and velocity (advective plus sinking).\\}

% {\color{red}
%This is correct.\\}

 \textit{But why is the flux at day 25 the important quantity? By this time, the large particles have had time to decay to a size where their sinking velocity is negligible, and therefore their contribution to the flux will be small.}

 {\color{blue}
 This is a good point. We have revised Fig 7 and 8 to now display the PDF of biomass fluxes integrated over the entire particle tracking experiment (i.e. 28 days). Our conclusions are not sensitive to whether the PDFs are for a specific day or for the entire simulation, because the respective contributions of the different size classes does not vary significantly over the course of the simulation. Showing day 25 of the simulation simplified the interpretation of the PDFs; in fact, the impact of remineralization on the PDFs is not as clear in the time-integrated PDFs. However, based on the reviewer's comment we have now replaced the figures with the time-integrated PDFs and  added an explanation in the text.\\}

@@

 \textit{But, what about all of the large particles that settled across the export horizon (100m) earlier in the simulation, while their sinking velocity is still high? Really, we should be interested in how much of the initial biomass in each size category has "escaped" through the export horizon by the end of the simulation, i.e. their time-integrated contribution to export.}

 {\color{blue}
Our study focuses on export fluxes rather than export through a horizon to avoid introducing subjectivity in defining an export horizon (see comment above).\\}

@@

{\color{blue}The text has been modified accordingly.\\}

\textit{Figure 7+8: It would be useful to point out either in the caption or axis label that the x axes are the vertical velocity combining both sinking and advective components, and that the velocity in the legends is the initial sinking velocity. This confused me for a few minutes.}

{\color{blue}Figure captions have been modified.\\}

\textit{Acknowledgments: Will the model output be archived for public access?}\\
{\color{blue} Due to the very large amount of model data necessary for this study ($>$ 1 TB), it is not possible to provide the data online. Instead, the source code used to conduct the physical model simulations is made publicly available on GitHub (\url{https://github.com/PSOM/V1.0/tree/master/code/NP_summer} and \url{https://github.com/PSOM/V1.0/tree/master/code/NP_winter}). The source code for particle tracking experiments is also available online \url{https://github.com/PSOM/offline_particle_tracking}. Finally, the routines used to extract the relevant data and produce the figures is available \url{https://github.com/matdever/Size-differentiated_Export_GBC/tree/master/figures/code}. This information is provided in the acknowledgements, with a citeable DOI.}

@@

\section*{Range of sinking speeds.}
\textit{The sinking speed examined by the authors are 0.025, 0.05, 1 and 5 m/d. All these values would be considered as "slow sinking rate" by the community. Yet, the manuscript concludes on the relative contribution of slow and fast sinking particles, which is misleading. It also means that the authors cannot really conclude about the relative role of particles that have sinking rates similar in magnitude or faster than submesoscale motions (i.e. 50-300 m/d).}

{\color{blue}Thank you for this comment. We have now clarified that we refer to particles as ``fast (or slow)'' sinking if their sinking speed is fast (or slow) compared to the vertical velocities in the flow.} \\

{\color{blue}
	The three sinking rates were defined based on having one class virtually non-sinking (0.025 m/day), one class within the range of $w$ modeled (1 m/day), and one class larger than $w$ modeled at submesoscale in the winter case (5 m/day). In fact, at any given time, at least 85\% of the modeled vertical velocity is smaller than 5 m/day -- our fastest sinking rate.
	%and an even larger percentage is sampled by the Lagrangian particles. For all intents and purposes, a 5 m/day sinking particle is ``fast" compared to the dynamical flow of the simulations.
	Particles with sinking speeds that greatly exceed the flow velocities would behave in a predictable way; their flux would be dominated by sinking.  The objective of the study is to capture that transitional part of the size spectrum. Station Papa is a relatively calm region, so submesoscale vertical velocities $w$ are of the order of 10 m/day at most. Other regions with stronger fronts would have $w\sim$ 100 m/day) and would affect a greater part of the particle size spectrum.\\

Please read the response to reviewer \#1 section for an even more in-depth justification of the range of sinking speeds. To ensure that this is clearer in the manuscript, we have modified the Introduction and the second paragraph of section 2.2.2.\\}

@@

\textit{The authors need to justify their choice, discuss the implications of this choice and explain how it informs the current view of the community on POC export. The authors should justify the narrow range of vertical velocity they explore. Prior observation-based studies emphasize the importance of particles sinking at slow rates ($<$ 10 m/d) but also those sinking at very fast rates similar in magnitude to submesoscale vertical motions (200-300 m/d) (e.g. Baker et al 2017, Riley et al 2016, Stuckel et al. 2017b). What are the reasons to look at only very slow sinking particles? Is it because of limitations related to the Stokes Law? Is it because the model is not adapted to look at faster sinking rates?}

{\color{blue}
	There are no analytic limitations in exploring the faster-sinking part of the particle sinking velocity spectrum. As outlined above, the choice of sinking rates is based on the dynamics of the region studied. Any other regions with stronger vertical motions at submesoscales could be explored with faster sinking particles. We believe the overarching conclusion would be the same: The 1D traditional paradigm fails to capture export for particles with sinking rates similar or smaller than the vertical velocity, especially when the spectrum slope is steeper. At Station Papa, this affects the range of particles sinking at $<$ 5 m/day, but in a place where relative vorticity is larger (e.g., gulf stream), and vertical velocities can reach the order of 100 m/day, then the range of particle size for which the 1D model fails would be greater. All of our results are put in perspective of the ratio between advective and sinking rates, which makes them applicable to other regions of the ocean. We have addressed this point even further in our response to another comment above (Major point \#2 of reviewer \#1), which led to additional text in the discussion section.\\}

\textit{By limiting their study to slow sinking particles, the authors target by design the particles that will be most sensitive to submesoscale dynamics (see Stukel et al) and exclude particles that sink with rates similar or faster than submesoscale motions and that can efficiently export at depth and participate to carbon sequestration.}

{\color{blue}
	As mentioned above, the range of sinking velocity is scaled to the environment, and is meant to encompass the range of velocities observed in that region. Sinking velocity far exceeding water vertical velocity can be simply computed using a 1D approximation. See above for more in-depth discussion\\}

 \textit{Indeed, submesoscale is largely trapped in the upper ocean and only have a limited impact on export at greater depth (see previous discussions of these effects in Stukel et al, Erikson et al and Resplandy et al). The authors should acknowledge these limitations and discuss their implications.\\}

{\color{blue} While submesoscale dynamics are strongest in the mixed layer, they have been proven to leak into the ocean interior, especially when coupled to a mesoscale circulation (see Ramachandran et al. 2014 in JGR and Ruiz et al. 2019 in JGR). Resplandy et al. 2019 explicitely mentions the fact that submesoscales dynamics are not resolved in the model used, and that the asymmetry associated with vertical velocityies at submesoscales  (i.e. the main mechanism leading to our conclusions) is not resolved (see Section 4.2 "Caveats and Limitations" in Resplandy et al.). A similar comment can be made for Erickson and Thompson 2018 (horizontal resolution is 2-4 km, so realistically not resolving processes at less than 10 km scales), and Stukel and Ducklow 2017 (stations are at most 10 km apart).
We do not believe that the study is biased by design, as the fastest sinking particle class (5 m/day) virtually follows the 1D gravitational model that would also apply to all faster-sinkin particle classes, and are therefore insensitive to the presence of submesoscale dynamics (as demonstrated in the study).\\}

@@

\textit{The author could introduce the study by acknowledging up front that slow sinking particles are the particles most impacted by submesoscale (as shown in previous papers) and this is why they are the focus of this paper that explores the sensitivity to size spectrum etc.}

{\color{blue}
	This is a good point. We trust that the modifications made to the introduction now reflect this key aspect of the paper. The point is reiterated in Section 2.2.2 as well.}

\section*{Remineralization and slower sinking particle contribution.}
\textit{The choice of some parameter appears arbitrary. I like the fact that the authors sweep the parameter space of the size spectrum ($\xi$ = 2, 3, 4). The choice of this parameter is however key in the conclusion that are drawn (contribution of slower-sinking particles , L557-558).}

{\color{blue}
	This parameter range is based on observational evidence cited in the text (L640), although not explicitly in section 2.2.3., where it would be most informative. We have modified the text in section 2.2.3 to better justify the range of $\xi$ used in this study. there is also a few sentences in Section 4.2 putting these values for the slope into perspective. \\} %, explaining that the exact value is a result of our approximations, but that the conclusion of the importance of constraining that slope remains valid, as the threshold is likely within the range of observed values for $\xi$.\\}

@@

\textit{Could you please present the case where the biomass spectrum slope is positive? Same as Figure 8 but with $\xi$ = 2 and contrast it with the case of $\xi$ = 4?\\}

{\color{blue}
Figure 8 has been modified to include both $\xi$ = 2 and $\xi$ = 4 cases in the presence of remineraliztion.\\}

@@

\textit{The effect of negative vs positive biomass spectrum slope is translated in your abstract by the rather vague "under specific conditions ..." (L27). Please try to clarify what this means in Layman terms in the abstract.}

{\color{blue}Text has been modified to address this comment.\\}

\textit{How do your results depend on the remineralization (0.13 d-1) length-scale? \\}

{\color{blue} We can only offer a hypothesis to answer that question, as the impacts of remineralization are non-linear and even counter-intuitive in the dynamically active submesoscale flows, and accumulate through time at an exponential rate (see Equation 9 and 10). In the absence of submesoscale dynamics, a back-of-the-envelope calculation that assumes $w_{tot} = w_{s}$ tells us that a  1\% change in the remineralization rate leads to a 0.2\% per day change in the vertical flux. The corresponding sensitivity in the presence of submesoscale dynamics is impossible to confidently predict without a thorough investigation involving a significant number of additional simulations.\\}

@@

\section*{Literature Survey and Discussion}
It is very concerning that the authors are missing key recent papers published on the subject, including observation-based papers that should be discussed with the author's modeling results. Please find below a list of relevant papers that should be included in introduction and/or discussion. This list is absolutely not exhaustive.

{\color{blue} Thank you for pointing out these studies, some of which are now cited in the manuscript. Some of those studies focus on, we believe, ocean dynamics at a different scale (and regime) and are not necessarily directly relevant. While useful for context, those were intentionally left out of the bibliography.\\}

@@

\section*{The introduction lacks some coherence. The different paragraphs are not clearly connected and the flow is rather tedious. It needs streamlining. }
\begin{itemize}
	\item	The second paragraph presents detailed theoretical arguments about particle size spectrum and sinking velocities.
	\item	The third paragraph list some previous results suggesting a role of submesoscale vertical velocities in exporting carbon. Note that numerous recent papers, including observation-based studies, are missing from this list (see below).
	\item	The fourth paragraph describe submesoscale frontogenesis.
	\item	The fifth paragraph repeat the idea that submesoscale can export POC.
	\item	The sixth paragraph add to the first paragraph on our knowledge about particle size and sinking speed. I would merge paragraphs 6 and 2. I would also strongly suggest to mention observations (paragraph 6) and what observed sinking speeds are (please add references for this. E.g. Baker et al 2017, Riley et al 2016 etc.). Then I would present the theoretical arguments (paragraph 2).
	\item	Paragraphs 8 and 7 should be merged with paragraph 7. I suggest to present what the aim of the study is (some of paragraph 8) before mentioning the processes that your model does not resolve (e.g. surface wave in paragraph 7)
\end{itemize}

{\color{red} Amala will tackle this part.}

\section*{Abstract}
The abstract is long and technical but at the same time vague in presenting the key results to the reader. For example, the following sentences list raw modeling results without hinting at the mechanistic drivers of this response in the model.
"a steeper particle size spectrum increases the relative contribution of smaller slow-sinking particles." "Implementing a remineralization scheme generally decreases the total amount of biomass exported[...]", "Under specific conditions, remineralization processes counter-intuitively enhance the role of slower-sinking particles."

{\color{blue}The abstract has been modified to improve clarity of the study's result.\\}

\section*{Section 2.2}
The method section is detailed and relatively clear except for section 2.2.3. To clarify this section, the author should give some contextual information about the different metrics (N, B etc.) and why they are presented to the reader.
\begin{itemize}
	\item Link to observational constraints on the slope of the size spectrum (see comment \#2)?\\
	{\color{blue} Range of typical values, along with the references, have been added to Section 2.2.3.\\}

### 2020-06-26 size_differentiated_export.tex
Another round of corrections appliued to the manuscript.
Addresses all remaining comments except for the suggested citations.

	%% ------------------------------------------------------------------------ %%
	%
	%  TITLE
	%
	%% ------------------------------------------------------------------------ %%
	\title{Size-differentiated Export in Different Dynamical Regimes in the Ocean}

@@

	%% ------------------------------------------------------------------------ %%
	%
	%  ABSTRACT
	%
	%% ------------------------------------------------------------------------ %%
	\begin{abstract}
		Export of Particulate Organic Carbon (POC) is  mainly driven by gravitational sinking. Thus, traditionally, it is thought that larger, faster-sinking particles make up most of the POC export flux. However, this need not be the case \change{in a dynamic oceanic flow field,}{for particles whose sinking speeds are comparable to the vertical velocities of a dynamic oceanic flow field} \change{where the ocean velocity}{that} can influence the descent rate of particles. Particles with different settling speeds \change{}{that can be affected by the flow} are released in two process-oriented model simulations of an upper ocean eddying flow \change{}{in the Northeast Pacific near Station Papa} to evaluate the impact of (1) ocean dynamics on the respective contribution of the different sinking-velocity classes to POC export, and (2) the particle number size-spectrum slope. The analysis reveals that the leading export mechanism changes from gravitationally-driven to advectively-driven as submesoscale dynamics become more \change{important}{active in the region}. The vertical velocity associated with submesoscale dynamics enhances the contribution of slower-sinking particles to POC export\change{. A steeper particle size spectrum, also increases the relative contribution of smaller, slower-sinking particles}{, especially where the relative abundance of small particles is large, as represented by a steep particle size-spectrum slope}. \change{Implementing a r}{R}emineralization \remove{scheme} generally decreases the total amount of biomass exported, but its impact is weaker in dynamical regimes where submesoscale dynamics are present and export is advectively-driven. \change{Under specific conditions}{In an advectively-driven export regime}, remineralization processes counter-intuitively enhance the role of slower-sinking particles to the point where these slower-sinking velocity classes dominate the export, therefore challenging the traditional paradigm for POC export. This study demonstrates that slow-sinking particles can be a significant contribution, and at times, even dominate the export flux. 
	\end{abstract}

@@

	Photosynthesis in the sunlit upper ocean and the production of Particulate Organic Carbon (POC) takes up dissolved inorganic carbon and facilitates the uptake of CO$_2$ from the atmosphere. The sinking of POC exports organic carbon from the upper ocean to the interior, leading to the sequestration of carbon \citep{Falkowski_1998} on timescales ranging from days to years depending on the sinking depth and  circulation. Understanding the mechanisms driving the export of POC from the ocean's surface to the interior is therefore crucial to better constrain Earth's carbon budget.

@@

	\subsubsection{Density and Biomass Spectra}
	\label{sec: equations_biomass}
	The slope $\xi$ of the size spectrum of particles \citep[also know as the Junge slope;][]{White_2015} is the slope of the log-log curve of particle number $N$ vs. particle radius $r$, where
	\begin{equation}
		N(r) = N_0 \left(\frac{r}{r_0}\right)^{-\xi}.
		\label{eq: powerlaw_radius}
	\end{equation}
	Here, $N_0$ and $r_0$ represent a reference particle number and radius, chosen arbitrarily. For small particles ($<$400 $\mu$m) and relatively low temperature ($<$15$^o$C), it has been shown that the relationship between particle radius $r$ and sinking velocity $w_s$ exhibits a range of variation and is difficult to determine empirically. Nevertheless, Stokes' law, where $w_s \propto r^2$, is often used as a lower-bound sinking velocity estimate \citep{Bach_2012}.

	Assuming a Stokes-like relationship, we can construct a particle sinking velocity spectrum $N(w_s)$ based on (\ref{eq: powerlaw_radius}), as
	\begin{equation}
		N(w_s) = N_0 \left(\frac{w_s}{w_{s_0}}\right)^{-\xi/2},
		\label{eq: powerlaw_velocity}
	\end{equation}
	where $w_{s_0}$ is the sinking speed of particles with radius $r_0$.
	For a specific slope and sinking-velocity class, an equivalent number of particles per simulated particle can be computed using (\ref{eq: powerlaw_velocity}) (See Figure \ref{fig: sinking_velocity_spectrum}). For example, using the largest sinking velocity class as a reference (i,.e., $w_{s_0} = 5$ m/day and $N_0=$1,971,717), and a spectral slope $\xi = 4$, each simulated particle with a sinking velocity of 0.025 m/day in fact represents 40,000 particles (Figure \ref{fig: sinking_velocity_spectrum}). The relative biomass of a particle in a specific sinking-velocity class, $B_p(w_s)$ can be estimated if the biomass is assumed to scale with the particle's volume. The relative biomass of one particle in a sinking-velocity class $w_s$ can therefore be computed as
	% FIG4
	\begin{figure}[ht]
		\centering
		\includegraphics[width = .49\linewidth]{Fig4b.png}
		\includegraphics[width = .49\linewidth]{Fig4a.png}
		\caption{Relative number of particles (left) and biomass (right) as a function of sinking velocity $w_s$. Sinking velocity spectrum are shown for three different Junge slope $\xi$: 2 (dotted), 3 (solid), and 2 (dashed). Colored squares indicate the sinking velocities of the three particle classes modeled: 0.025 m/day (red), 1 m/day (green), and 5 m/day (blue).}
		\label{fig: sinking_velocity_spectrum}
	\end{figure}
	\begin{equation}
		B_p(w_s) = B_p(w_{s_0})\left(\frac{w_s}{w_{s_0}}\right)^{3/2}
		\label{eq: biomass_realparticle}
	\end{equation}
	where $B_p(w_{s_0})$ is the biomass of a particle in the sinking velocity class $w_{s_0}$. The total biomass associated with one simulated particle can be obtained by scaling (\ref{eq: biomass_realparticle}) by the ratio $N(w_s)/N_0$:
	\begin{equation}
		B(w_s) =  B_0\left(\frac{w_s}{w_{s_0}}\right)^{3/2}\frac{N(w_s)}{N_0}
		\label{eq: biomass_simulatedparticle}
	\end{equation}
	where $B_0 = B_p(w_{s_0})$. Combining (\ref{eq: powerlaw_velocity}) and (\ref{eq: biomass_simulatedparticle}) yields an expression relating the biomass associated with a simulated particle for a specific sinking-velocity class and the spectral slope (Figure \ref{fig: sinking_velocity_spectrum}):
	\begin{equation}
		B(w_s) = B_0\left(\frac{w_s}{w_{s_0}}\right)^{\frac{3-\xi}{2}}.
		\label{eq: biomassjungeslope}
	\end{equation}
	Using the same example as before where $\xi = 4$, if the amount of biomass associated with one simulated particle in the 5 m/day sinking-velocity class is taken as $B_0 = 1$, then one simulated particle sinking at 0.025 m/day contains 14.14 units of biomass and a single particle contains $14.14/40,000 =3.5\times10^{-4}$ units of biomass (see Figure \ref{fig: sinking_velocity_spectrum}). This normalized formulation of particle number and biomass (see Equations (\ref{eq: powerlaw_velocity}) and (\ref{eq: biomassjungeslope})) has the advantage that the impact of spectral slope on the relative export of biomass can be quantified without needing a large number of particle-tracking experiments, where the number of seeded particles would vary to account for the different spectral slopes. For the purpose of this study, only the relative amount of biomass is relevant. For simplicity, we define a normalized biomass unit for $\xi =3$ as $B_0=$ 1. The values taken by $B_0$ for other Junge slopes $\xi$ are computed under the condition that the total amount of biomass is kept constant (Figure \ref{fig: sinking_velocity_spectrum}b).

@@

	%FIG6
	\begin{figure}[ht!]
		\centering
		\includegraphics[width = .8\linewidth]{Fig6.png}
		\caption{[left] 
			The median depth anomaly of particles with a sinking speed (a) 0.025 m/d, (b) 1 m/d, (c) 5 m/d within each grid cell for the winter case 25 days after particles are released. The `depth anomaly' is with respect to the `expected' sinking depth (= sinking speed $\times$ time since release). Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected, based on a 1D gravitational model where $z = w_s\times t$. [right] (d) Probability Distribution Function (PDF) of particles as a function of depth for each velocity class. The winter distribution is shown as thick lines, while the summer distribution is represented by the shaded regions. Triangle markers indicate the expected depth of particles after 25 days based on the 1D gravitational model, which is used as a reference to compute the depth anomalies. Release depth is indicated by the thick dashed line.}	
		\label{fig: particle_depth_distribution}
	\end{figure}

>>>>

	%% ------------------------------------------------------------------------ %%
	%
	%  TITLE
	%
	%% ------------------------------------------------------------------------ %%
	\title{Size-differentiated Export \add{Flux} in Different Dynamical Regimes in the Ocean}

@@

	%% ------------------------------------------------------------------------ %%
	%
	%  ABSTRACT
	%
	%% ------------------------------------------------------------------------ %%
	\begin{abstract}
		Export of Particulate Organic Carbon (POC) is  mainly driven by gravitational sinking. Thus, traditionally, it is thought that larger, faster-sinking particles make up most of the POC export flux. However, this need not be the case \change{in a dynamic oceanic flow field,}{for particles whose sinking speeds are comparable to the vertical velocities of a dynamic oceanic flow field} \change{where the ocean velocity}{that} can influence the descent rate of particles. Particles with different settling speeds \change{}{that can be affected by the flow} are released in two process-oriented model simulations of an upper ocean eddying flow \change{}{in the Northeast Pacific near Station Papa} to evaluate the impact of (1) ocean dynamics on the respective contribution of the different sinking-velocity classes to POC export, and (2) the particle number size-spectrum slope. The analysis reveals that the leading export mechanism changes from gravitationally-driven to advectively-driven as submesoscale dynamics become more \change{important}{active in the region}. The vertical velocity associated with submesoscale dynamics enhances the contribution of slower-sinking particles to POC export\change{. A steeper particle size spectrum, also increases the relative contribution of smaller, slower-sinking particles}{by a factor ranging from 3 to 10, especially where the relative abundance of small particles is large, as represented by a steep particle size-spectrum slope}. \change{Implementing a r}{R}emineralization \remove{scheme} generally decreases the total amount of biomass exported, but its impact is weaker in dynamical regimes where submesoscale dynamics are present and export is advectively-driven. \change{Under specific conditions}{In an advectively-driven export regime}, remineralization processes counter-intuitively enhance the role of slower-sinking particles to the point where these slower-sinking velocity classes dominate the export, therefore challenging the traditional paradigm for POC export. This study demonstrates that slow-sinking particles can be a significant contribution, and at times, even dominate the export flux.
	\end{abstract}

@@

	Photosynthesis in the sunlit upper ocean and the production of Particulate Organic Carbon (POC) takes up dissolved inorganic carbon and facilitates the uptake of CO$_2$ from the atmosphere. The sinking of POC exports organic carbon from the upper ocean to the interior, leading to the sequestration of carbon \citep{Falkowski_1998} on timescales ranging from days to years depending on the sinking depth and  circulation. %Understanding the mechanisms driving the export of POC from the ocean's surface to the interior is therefore crucial to better constrain Earth's carbon budget.

@@

	\subsubsection{Density and Biomass Spectra}
	\label{sec: equations_biomass}

	\add{To quantify vertical export fluxes, both the distribution of the number of particles and the associated biomass can be modeled based on two main variables: the particles' radii and the rate at which the number of particles changes with respect to the size. The particle number is modeled using a power-law function as a function of size that is driven by the paramater $\xi$.} This slope $\xi$ of the size spectrum of particles \citep[also know as the Junge slope;][]{White_2015} is the slope of the log-log curve of particle number $N$ vs. particle radius $r$, where
	\begin{equation}
		N(r) = N_0 \left(\frac{r}{r_0}\right)^{-\xi}.
		\label{eq: powerlaw_radius}
	\end{equation}
	Here, $N_0$ and $r_0$ represent a reference particle number and radius, chosen arbitrarily. \add{Typical values for $\xi$ derived from both in-situ observations and satellite data have been reported to range from 3 to 6} \citep[][Z. Xiaodong, personal communication]{Kostadinov_2009, White_2015}. For small particles ($<$400 $\mu$m) and relatively low temperature ($<$15$^o$C), it has been shown that the relationship between particle radius $r$ and sinking velocity $w_s$ exhibits a range of variation and is difficult to determine empirically. Nevertheless, Stokes' law, where $w_s \propto r^2$, is often used as a lower-bound sinking velocity estimate \citep{Bach_2012}.

	Assuming a Stokes-like relationship, we can construct based on (\ref{eq: powerlaw_radius}) a particle sinking velocity spectrum $N(w_s)$, as \add{a function of the Junge slope $\xi$:}
	\begin{equation}
		N(w_s) = N_0 \left(\frac{w_s}{w_{s_0}}\right)^{-\xi/2},
		\label{eq: powerlaw_velocity}
	\end{equation}
	where $w_{s_0}$ is the sinking speed of particles with radius $r_0$.
	For a specific slope and sinking-velocity class, an equivalent number of particles per simulated particle can be computed using (\ref{eq: powerlaw_velocity}) (See Figure \ref{fig: sinking_velocity_spectrum}). For example, using the largest sinking velocity class as a reference (i,.e., $w_{s_0} = 5$ m/day and $N_0=$1,971,717), and a spectral slope $\xi = 4$, each simulated particle with a sinking velocity of 0.025 m/day in fact represents 40,000 particles (Figure \ref{fig: sinking_velocity_spectrum}). The relative biomass of a particle in a specific sinking-velocity class, $B_p(w_s)$ can be estimated if the biomass is assumed to scale with the particle's volume. The relative biomass of one particle in a sinking-velocity class $w_s$ can therefore be computed as
	% FIG4
	\begin{figure}[ht]
		\centering
		\includegraphics[width = .49\linewidth]{Fig4b.png}
		\includegraphics[width = .49\linewidth]{Fig4a.png}
		\caption{Relative number of particles (left) and biomass (right) as a function of sinking velocity $w_s$. Sinking velocity spectrum are shown for three different Junge slope $\xi$: 2 (dotted), 3 (solid), and 2 (dashed). Colored squares indicate the sinking velocities of the three particle classes modeled: 0.025 m/day (red), 1 m/day (green), and 5 m/day (blue).}
		\label{fig: sinking_velocity_spectrum}
	\end{figure}
	\begin{equation}
		B_p(w_s) = B_p(w_{s_0})\left(\frac{w_s}{w_{s_0}}\right)^{3/2}
		\label{eq: biomass_realparticle}
	\end{equation}
	where $B_p(w_{s_0})$ is the biomass of a particle in the sinking velocity class $w_{s_0}$. The total biomass associated with one simulated particle can be obtained by scaling (\ref{eq: biomass_realparticle}) by the ratio $N(w_s)/N_0$:
	\begin{equation}
		B(w_s) =  B_0\left(\frac{w_s}{w_{s_0}}\right)^{3/2}\frac{N(w_s)}{N_0}
		\label{eq: biomass_simulatedparticle}
	\end{equation}
	where $B_0 = B_p(w_{s_0})$. Combining (\ref{eq: powerlaw_velocity}) and (\ref{eq: biomass_simulatedparticle}) yields an expression relating the biomass associated with a simulated particle for a specific sinking-velocity class and the spectral slope (Figure \ref{fig: sinking_velocity_spectrum}):
	\begin{equation}
		B(w_s) = B_0\left(\frac{w_s}{w_{s_0}}\right)^{\frac{3-\xi}{2}}.
		\label{eq: biomassjungeslope}
	\end{equation}
	Using the same example as before where $\xi = 4$, if the amount of biomass associated with one simulated particle in the 5 m/day sinking-velocity class is taken as $B_0 = 1$, then one simulated particle sinking at 0.025 m/day contains 14.14 units of biomass and a single particle contains $14.14/40,000 =3.5\times10^{-4}$ units of biomass (see Figure \ref{fig: sinking_velocity_spectrum}). This normalized formulation of particle number and biomass (see Equations (\ref{eq: powerlaw_velocity}) and (\ref{eq: biomassjungeslope})) has the advantage that the impact of spectral slope on the relative export of biomass can be quantified without needing a large number of particle-tracking experiments, where the number of seeded particles would vary to account for the different spectral slopes. For the purpose of this study, only the relative amount of biomass is relevant. For simplicity, we define a normalized biomass unit for $\xi =3$ as $B_0=$ 1. The values taken by $B_0$ for other Junge slopes $\xi$ are computed under the condition that the total amount of biomass is kept constant (Figure \ref{fig: sinking_velocity_spectrum}b).

@@

	%FIG6
	\begin{figure}[ht!]
		\centering
		\includegraphics[width = .8\linewidth]{Fig6.png}
		\caption{[left]
			The median depth anomaly of particles with a sinking speed (a) 0.025 m/d, (b) 1 m/d, (c) 5 m/d within each grid cell for the winter case 25 days after particles are released. The `depth anomaly' is with respect to the `expected' sinking depth (= sinking speed $\times$ time since release). Blue (red) grid cells indicate that the median depth of particles in this cell is deeper (shallower) than expected, based on a 1D gravitational model where $z = w_s\times t$. [right] (d) Probability Distribution Function (PDF) of particles as a function of depth for each velocity class \add{(red = 0.025 m/day; green = 1 m/day; blue = 5 m/day)}. The winter distribution is shown as thick lines, while the summer distribution is represented by the shaded regions. Triangle markers indicate the expected depth of particles after 25 days based on the 1D gravitational model, which is used as a reference to compute the depth anomalies. Release depth is indicated by the thick dashed line.}
		\label{fig: particle_depth_distribution}
	\end{figure}
